Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-09-08 scripts/MouseSexDiffVar_05_2020.Rmd
Added some ne descriptive stats to the very first trait based 218 meta-analysis table. Just added rows. Problems rendering though in places of script that I've not touched. Not sure whats up L2647 mark

---
title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
  and statistical implications'
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior,
  Daniel Noble, & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
  word_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
  bookdown::html_document2:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 6
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

```{r packages1, echo = FALSE, eval = TRUE, messages = FALSE}
library(pacman)
pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
```

@@

# Create dataframe to store results
results_alltraits_grouping <- 
    data.frame(tibble(id = 1:n, 
           lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, lnCVR_se=0, 
            lnVR=0,  lnVR_lower=0,  lnVR_upper=0, lnVR_se=0, 
            lnRR=0,  lnRR_lower=0,  lnRR_upper=0, lnRR_se=0, 
           sampleSize=0, trait=0))

@@

      results_alltraits_grouping[t, 2:14] <- c(f(cvr), f(cv), f(means), k=means$k)
      results_alltraits_grouping[t, 15]   <- unique(results$trait)
    },
    error = function(e) {
      cat("ERROR :", t, conditionMessage(e), "\n")
    }
  )
}
```

@@

```{r cleanMeta1}
results_alltraits_grouping2 <- 
  results_alltraits_grouping %>%

@@

@@

```{r Table2_Meta1}
# Here we double check numbers of trait parameters in the dataset
meta1 <- meta_clean 
# length(unique(meta1$procedure)) #18
# length(unique(meta1$GroupingTerm)) #9
# length(unique(meta1$parameter_group)) # 148 levels. To be used as grouping factor for meta-meta-analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
# length(unique(meta1$parameter_name)) #218
# and prepare the dataset for second-order meta-analysis
meta1_sub <- meta1 %>%
  # Add summary of number of parameter names in each parameter group
  group_by(parameter_group) %>%
  mutate(par_group_size = length(unique(parameter_name)), 
         sampleSize = as.numeric(sampleSize)) %>% 
  ungroup() %>% 
  # Create subsets with > 1 count (par_group_size > 1)
  filter(par_group_size > 1) # 90 observations

@@

           meta1_sub <- subset(meta1,par_group_size >1) # 90 observations   
meta1_sub$sampleSize <- as.numeric(meta1_sub$sampleSize)

@@

# Final fixed effects meta-analyses within grouping terms, with SE of the estimate

@@

# Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate

@@

overall2 <- bind_rows(extract_trait(overall1, "Behaviour"), 
                      extract_trait(overall1, "Morphology"), 
                      extract_trait(overall1, "Metabolism"), 
                      extract_trait(overall1, "Physiology"), 
                      extract_trait(overall1, "Immunology"), 
                      extract_trait(overall1, "Hematology"), 
                      extract_trait(overall1, "Heart"), 
                      extract_trait(overall1, "Hearing"), 
                      extract_trait(overall1, "Eye"), 
                      All)

@@

heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate

@@

plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)

@@

overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 

@@

plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)

@@

overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 

@@

overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

# Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate

@@

overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

>>>>

---
title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
  and statistical implications'
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior,
  Daniel Noble, & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 6
    toc_float: yes
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
  word_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
  bookdown::word_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

```{r packages1, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
library(pacman)
pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
```

@@

# Create dataframe to store results
results_alltraits_grouping <- 
    data.frame(tibble(id = 1:n, 
           lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, lnCVR_se=0, lnCVR_I2=0,
            lnVR=0,  lnVR_lower=0,  lnVR_upper=0, lnVR_se=0, lnVR_I2=0,
            lnRR=0,  lnRR_lower=0,  lnRR_upper=0, lnRR_se=0, lnRR_I2=0,
           k=0, trait=0, male_N = 0, female_N=0, min_male_N = 0, max_male_N = 0, mean_male_N = 0,
              min_female_N = 0, max_female_N = 0, mean_female_N = 0))

@@

      extract_I2 <- function(mod){
                  sigma2 <- mod$sigma2
                       w <- mod$vi
                       k <- mod$k

                  sigmaM <- sum(w * (k-1)) / (sum(w)^2 - sum(w^2))

                    I2_tot <- round(sum(sigma2) / sum(sigma2 + sigmaM), digits = 3)*100
                  return(I2_tot)
      }

      results_alltraits_grouping[t, c(2:17,19:26)] <- c(f(cvr),lnCVR_I2 = extract_I2(cvr), f(cv), lnVR_I2 = extract_I2(cv), f(means), lnRR_I2 = extract_I2(means), k=means$k, male_N = sum(results$male_n_ind), female_N = sum(results$female_n_ind), min_male_N = min(results$male_n_ind), max_male_N = max(results$male_n_ind), mean_male_N = mean(results$male_n_ind),
                                                        min_female_N = min(results$female_n_ind), max_female_N = max(results$female_n_ind), mean_female_N = mean(results$female_n_ind))
      results_alltraits_grouping[t, 18]   <- unique(results$trait)
    },
    error = function(e) {
      cat("ERROR :", t, conditionMessage(e), "\n")
    }
  )
}

@@

```{r cleanMeta1, results='hide'}
results_alltraits_grouping2 <- 
  results_alltraits_grouping %>%

@@

# Summary of the cleaned data for 218 traits
  range(meta_clean$male_N)
  range(meta_clean$female_N)
  range(meta_clean$lnCVR_I2)
  range(meta_clean$lnVR_I2)
  range(meta_clean$lnRR_I2)
  range(meta_clean$k)
  mean(meta_clean$mean_male_N)
  range(meta_clean$min_male_N)
  median(meta_clean$mean_male_N)
  sd(meta_clean$mean_male_N)
  sd(meta_clean$mean_male_N) / sqrt(length(meta_clean$mean_male_N))
  mean(meta_clean$mean_female_N)
  median(meta_clean$mean_female_N)
  range(meta_clean$min_female_N)
  sd(meta_clean$mean_female_N)
  sd(meta_clean$mean_female_N) / sqrt(length(meta_clean$mean_female_N))

@@

```{r Table2_Meta1}
# Here we double check numbers of trait parameters in the dataset
meta1 <- meta_clean 
# length(unique(meta1$procedure)) #18
# length(unique(meta1$GroupingTerm)) #9
# length(unique(meta1$parameter_group)) # 148 levels. To be used as grouping factor for meta-meta-analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
# length(unique(meta1$parameter_name)) #218
# and prepare the dataset for second-order meta-analysis
meta1_sub <- meta1 %>%
  # Add summary of number of parameter names in each parameter group
  group_by(parameter_group) %>%
  mutate(par_group_size = length(unique(parameter_name)), 
         sampleSize = as.numeric(k)) %>% 
  ungroup() %>% 
  # Create subsets with > 1 count (par_group_size > 1)
  filter(par_group_size > 1) # 90 observations

@@

           meta1_sub <- subset(meta1,par_group_size >1) # 90 observations   
meta1_sub$sampleSize <- as.numeric(meta1_sub$k)

@@

# Final random effects meta-analyses within grouping terms, with SE of the estimate

@@

# Final random effects meta-analyses ACROSS grouping terms, with SE of the estimate

@@

overall2 <- rbind(extract_trait(overall1, "Behaviour"), 
                      extract_trait(overall1, "Morphology"), 
                      extract_trait(overall1, "Metabolism"), 
                      extract_trait(overall1, "Physiology"), 
                      extract_trait(overall1, "Immunology"), 
                      extract_trait(overall1, "Hematology"), 
                      extract_trait(overall1, "Heart"), 
                      extract_trait(overall1, "Hearing"), 
                      extract_trait(overall1, "Eye"), 
                      All)

@@

heterog4 <- rbind(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

# **Final random effects meta-analyses within grouping terms, with SE of the estimate

@@

plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing)

@@

overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>% 

@@

plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing)

@@

overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>% 

@@

overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

overall4.female.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

overall4.perc <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

# Final random effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate

@@

overall4.male.perc <- rbind(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
